---
output:
---

# Instroductory analysis
Situation: people going inside and outside of a discoteque through two gates
```{r}
data <- read.csv("data.csv")
library(dplyr)
library(tidyr)
barplot(table(data$receptor), main="Events at each receptor")
num_macs <- count(data, MAC)$n
mean(num_macs)
sd(num_macs)
qqnorm(num_macs)
qqline(num_macs)
```

## Macs distribution
It seems that the distribution the repetition of macs is a bit right-skewed. Seeing it in a histogramm, we can confirm this:
```{r}
hist(num_macs, freq = F)
lines(seq(min(num_macs), max(num_macs), 0.1) ,dnorm(seq(min(num_macs), max(num_macs), by = 0.1),  mean = mean(num_macs), sd=sd(num_macs)))
```
Since this data is random and each timestamp a mac is generated with an uniform probability between all posibilities, and since the times a mac shows up is a sum of uniforms, due to the law of big numbers we can asume normality. 
TODO: normality test

## Devices appearing only once
```{r}
# Only once
sum(num_macs==1)
# More than once
sum(num_macs!=1)
```

# Evolution of people inside the system

```{r}
# new column: is entering (T or F)
grouped <- data %>% group_by(MAC) %>%  mutate(
  entering=as.logical(rank(timestamp) %% 2))
# Check if column "entering" changes each time a MAC appears
grouped[(grouped$MAC=="90b7"),]
# Amount of people in each timestamp: sum of "T" until then
accumulated <- ungroup(grouped) %>% mutate(
  inside=cumsum(entering)-cumsum(!entering))
head(accumulated,40)
# Diplays the state of the system each time 90b7 appears
accumulated[(accumulated$MAC=="90b7"),]
smoothScatter(accumulated$timestamp, accumulated$inside, xlab = "Timestamp", ylab="Amount of devices", main="Devices inside the system")

```

# Distribution of time inside the system
```{r}
  # data %>% filter(timestamp <= ts) %>% group_by(MAC)
time_cum <- function(data, mac, ts){
  mac_info <- data %>% select(timestamp, MAC, entering) %>% filter(timestamp <= ts & MAC == mac)
  time_inside <- NULL
  if(last(mac_info$entering)==FALSE){
    # that is, equal size of vectors, out of the system
    time_inside <- subset(mac_info, entering==F,select=timestamp) - subset(mac_info, entering==T, select=timestamp)
  } else{
    # that is, unequal size of vector, must add last timestamp to the data frame
    # last timestamp: that of the desired time window, or the whole meassure
    time_inside <- rbind(subset(mac_info, entering==F,select=timestamp),min(max(data$timestamp),ts))- subset(mac_info, entering==T, select=timestamp)
  }
  time_inside
}
# using grouped causes infite processing time
time_cum(accumulated, "cafe", 1000000)
# only 1000 macs are used, the full set is too big and takes too long
mac_list <- sample_n(unique(accumulated), 1000)$MAC
vec <- mapply(time_cum,mac_list, MoreArgs = list(data=accumulated,ts=10000000)) 
hist(sapply(vec,sum), main = "Time inside the system", xlab="seconds", freq = T)
```


