---
title: "Static report"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

# Whole data mac count
```{r}
source("./static-analysis.R")
# mac_data <- read_capture_file("~/Desktop/DTEC_no_associated.csv")
mac_data <- read_capture_server("http://ec2-54-72-240-166.eu-west-1.compute.amazonaws.com:3000/macs")
fixed_data <- filter(mac_data, type == "fixed")
#> names(fixed_data)

## [1] "mac"    "device" "ID"     "time"   "type"  
mac_distro <- mac_count_distribution(fixed_data, mac_col = "mac")
summary(mac_distro$mac_count)
```
Datta summary shows most macs appear few times, less than 80 times. Histogramm will display just data under the 0.8 quantile.
```{r}
q80 <- quantile(mac_distro$mac_count, probs = 0.8)
hist(filter(mac_distro, mac_count <= q80)$mac_count, xlab = "Mac appearances",
     main = "Mac count distribution Q_80")
```

# Time between bursts.

From now on we will sample data in intervals of equal length, and then operate. All plots show the result of this opetations divided by intervals.

As a rule of thumb we need to provide at least 30 different meassurements for any calculation/distribution to make it valid. Therefore, be L our whole timespan for the dataset, and T our interval length, **L/T >= 30**. At the same time, T must be big enough to let as many devices as possible emit one probe request.

```{r}
t_burst <- time_between_bursts(fixed_data, "mac", "time")
# histograms and means need round values, not dates
burst_diff <- t_burst$avg_secs
# L: time range for the meassurements
L <- as.numeric(difftime(max(mac_data$time),min(mac_data$time), units="secs"))
# T: sampling interval. Must guarantee at least 30 samples
T <- max(burst_diff)
if(L/T < 30){
  T <- L/30
}
round_secs <- paste(floor(T), "secs")
```

The interval length for all operations is `r L` seconds, which guaranties 30 intervals for sampling

## Distribution

```{r}
hist(burst_diff, main="Average time between bursts", prob=T)
legend("topright", col = c("blue", "red"), lty=c(1,1), legend = c("Kernel Estimation", "Exponential Distribution"))
lines(density(burst_diff), col="blue")
# Plotting theoretical exponential density function
lines(dexp(seq(0, max(burst_diff), by=1), rate = 1/mean(burst_diff)), 
      col="red")
burst_avg <- mean(burst_diff)
```

Histogram and kernel estimation shows an exponential distribution for time between arrivals for fixed adresses. Therefore, we can asume that arrivals are a Poisson proccess, and all its properties: independence in disjunct intervals, iid, independent sum of processes.

# Random Macs estimation

Time between arrivals for fixed addresses follows an exponential distribution with average `r burst_avg`, and a lambda parameter `r 1/burst_avg` (the inverse of the average). This lambda is the parameter for the Poisson distribution of the arrivals.

We can assume that random macs follow the same distribution with the same parameters. Therefore, for a series of disjunct intervals of length T, the probability of having n arrivals is **insert Poisson distribution formulae**, for one source. Its expected value E(X) is **E(x) =  lambda*T**. If there are N devices, and because of the sum of independent poisson variables, the expected number of observations should be that, times the sources: **E(x) = N*lambda*T**, which we could approximate with a large set of samples thanks to the law of large numbers.
```{r}
lambda = 1/burst_avg
random_macs_observations <- mac_data %>% filter(type == "random") %>%
  distinct(mac, time) %>% split_in_intervals(., "time", round_secs) %>%
  group_by(time) %>% count(mac) %>% summarise(random_count = sum(n))
lambda = 1/burst_avg
N = mean(random_macs_observations$random_count)/lambda/T
# random_macs_observations <- split_in_intervals(random_macs_observations, "time", 
  #   group_by_(time_col) %>% count_(mac_col) %>% summarise(dev_count = sum(n))
  # counted[[time_col]] <- as.POSIXct(counted[[time_col]])
  # counted
```


 
# Probe Requests per time interval. 
Plots packets captured by the antennass, that is, different macs seen per interval. as well as its distribution. Returns same results as IPYNotebook function origin_activity.

```{r}
interval_mac_count <- count_macs_interval(fixed_data, "time", "mac", round_secs)
plot_date_count(interval_mac_count, "time", "mac_count", round_secs)
hist(interval_mac_count$mac_count, main = "Probe Request Count Distribution")
# TODO: add legend (red = mean), function = plot histogramm with mean
abline(v = mean(interval_mac_count$mac_count), col = "red")
```

# System occupation: devices meassured by interval
Counts each different mac per interval to obtain the total amount of devices. Plots its distribution. Red line: mean, i.e, average ocupation of devices in our antenna range in that interval

Interval chosen: average time burst. A more precise value could be chosen (see time burst calculation).

```{r}
device_count <- count_devices_interval(fixed_data, "time", "mac", round_secs)
plot_date_count(device_count, "time", "device_count", round_secs)
hist(device_count$device_count, main = "System Occupation Distribution")
# TODO: add legend (red = mean), function = plot histogramm with mean
abline(v = mean(device_count$device_count), col = "red")
```

## New devices per interval
```{r}
new_devs_count <- count_new_devices_interval(fixed_data, "time", "mac", round_secs)
plot_date_count(new_devs_count, "time", "dev_count", round_secs)
```

## Cumsum: aggregate of new devices
```{r}
devs_evolution <- devices_accumulated(new_devs_count, "mac_count", "time")
# note: time interval only affects plot, not calculation
plot_date_count(devs_evolution, "time", "devs_cumsum", "100 sec", geom_line())
```

# How many devices are generating the random macs?
We will use a regression. We have previously obtained the average time between bursts for each mac. 

We need to obtain a threshold called T_avg. It should be the minimum time in which, on average, a device emits its mac only once. Therefore we can assume that all different macs in that interval correspond to different devices. For now, a small quantile suffices. Something better should be done (biggest interval that guarantees no repetitions, with some tolerance to get more data)

We are also asumming that devices do not emmit both kind of macs at the same time

We count random and fixed macs in each of the intervals, and pair the values as (N_random, N_fixed). A regression is applied to the whole set of pairs, thus obtaining the f(N_fixed) = devices_random

About final report: say in LPRO presentation that T_avg would be more precise if it was computed considered which devices form the market emmit random macs
```{r}
type_count <- binned_mac_pairs(mac_data, "time", "10 secs", t_burst$mac)
random_fixed_reg <- lm(random ~ fixed, data = type_count)
summary(random_fixed_reg)
plot(type_count$random ~ type_count$fixed, main = "Regression",
     xlab = "Devices emitting fixed Macs", ylab = "Devices emitting Random Macs")
abline(random_fixed_reg, col = "red")

```

There is no correlation between random and fixed probe requests. Our idea is not valid